An FMI-Based Initialization Plugin for INTO-CPS Maestro 2\thanks{We are grateful to the Poul Due Jensen Foundation, which has supported the establishment of a new Centre for Digital Twin Technology at Aarhus University. Finally, we thank the reviewers for the thorough feedback.}

### 2020-11-13 paper.tex
fix bib.bib
Updates from Overleaf

\usepackage{graphicx}
\usepackage{ae,aecompl}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amstext}
\usepackage{bm} 
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{siunitx}
\usepackage{mathrsfs}
\usepackage{wrapfig}
%\usepackage{minted}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{semantic}
\usepackage[dvipsnames]{xcolor}
\usepackage{paralist}
\usepackage{cite}
\usepackage[capitalise,nameinlink]{cleveref}
\usepackage{url}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{environ}
\usepackage{filecontents}
\usepackage{todonotes}
\usepackage{cleveref}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\input{commands}
\input{case_study_results}

@@

%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Simon Thrane Hansen\inst{1} \and
Casper Thule\inst{1} \and
Cláudio Gomes \inst{1}}
%
\authorrunning{S. Thrane et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule, claudio.gomes\}@eng.au.dk\}}}
%

>>>>

\usepackage{graphicx}
\usepackage{ae,aecompl}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amstext}
\usepackage{bm} 
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{siunitx}
\usepackage{mathrsfs}
\usepackage{wrapfig}
%\usepackage{minted}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{semantic}
\usepackage[dvipsnames]{xcolor}
\usepackage{paralist}
\usepackage{cite}
\usepackage[capitalise,nameinlink]{cleveref}
\usepackage{url}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{environ}
\usepackage{filecontents}
\usepackage{todonotes}
\usepackage{cleveref}
\usepackage{listings}
\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\includegraphics[width=10pt]{images/orcid.png}}}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\input{commands}
\input{case_study_results}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

@@

%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Simon Thrane Hansen\inst{1} \orcidID{0000-0002-3796-4319} \and
Casper Thule\inst{1} \orcidID{0000-0001-6606-9236} \and
Cláudio Gomes \inst{1} \orcidID{0000-0003-2692-9742}}
%
\authorrunning{S. Thrane et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule, claudio.gomes\}@eng.au.dk\}}}
%
